The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex
modify the section title SVM to SVM-GA, also Naive Bayes classifier to Naive Bayes classifier-GA

\section{SVM}
  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
  data is non-linearly separable. 
  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
  the occurrence of non-linear separability: 
	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
  not have binary class labels. 
  Based on \cite{santhanam2015application}, we can use genetic algorithm (GA) to achieve finding better hyperplanes. The following are the 
  steps to find the hyperplane using a GA: Firstly, decide the level of generations ($l$), population size ($n$), 
  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
  is found.

@@

\section{Naive Bayes classifier}
  Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 
  $i$-th class is $P(C_k\mid \bf{x})$ where $C_k$ is the event that data points $\bf{x}=(x_1,\cdots,x_n)$ belongs to $k$-th class.
  By using Bayes' theorem, the probability can be rewritten as 
  \begin{equation}
    \label{eqn:bayes}
    P(C_k\mid x)=\frac{P(C_k)P(\bf{x}\mid C_k)}{P(\bf{x})}
  \end{equation}
  In partice, 
  there is interest only in the numerator of that fraction, because the denominator does not depend on $C_k$ and the values of the 
  features that are given, so the denominator is effectively constant. 
  Then, by chain rule of conditional probability, the numerator of Eq. \ref{eqn:bayes} can be rewritten as
  \begin{equation}
    \label{eqn:rebayes}
    \begin{split}
      &P(C)P(x_1\mid C_k)P(x_2,\cdots,x_n\mid C_k,x_1)
      \\&=\cdots
      \\&=P(C)P(x_1\mid C_k)\cdots P(x_n\mid C_k,x_1,\cdots,x_{n-1})
    \end{split}
  \end{equation}

>>>>

\section{SVM-GA}
  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
  data is non-linearly separable. 
  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
  the occurrence of non-linear separability: 
	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
  not have binary class labels. 
  Based on \cite{santhanam2015application}, we can use genetic algorithm (GA) to achieve finding better hyperplanes. The following are the 
  steps to find the hyperplane using a GA: Firstly, decide the level of generations ($l$), population size ($n$), 
  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
  is found.

@@

\section{Naive Bayes classifier-GA}
  Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 
  $i$-th class is $P(C_k\mid \bf{x})$ where $C_k$ is the event that data points $\bf{x}=(x_1,\cdots,x_n)$ belongs to $k$-th class.
  By using Bayes' theorem, the probability can be rewritten as 
  \begin{equation}
    \label{eqn:bayes}
    P(C_k\mid x)=\frac{P(C_k)P(\bf{x}\mid C_k)}{P(\bf{x})}
  \end{equation}
  In partice, 
  there is interest only in the numerator of that fraction, because the denominator does not depend on $C_k$ and the values of the 
  features that are given, so the denominator is effectively constant. 
  Then, by chain rule of conditional probability, the numerator of Eq. \ref{eqn:bayes} can be rewritten as
  \begin{equation}
    \label{eqn:rebayes}
    \begin{split}
      &P(C)P(x_1\mid C_k)P(x_2,\cdots,x_n\mid C_k,x_1)
      \\&=\cdots
      \\&=P(C)P(x_1\mid C_k)\cdots P(x_n\mid C_k,x_1,\cdots,x_{n-1})
    \end{split}
  \end{equation}
